In the Crucible: Massive Compact Galaxies with High-Velocity Outflows and Eddington-Limited Star Formation

### 2012-04-20 trunk/tex/sigmasfr/ms.tex
cut references, modified figure 1

Galactic winds are ubiquitous in star-forming galaxies at all
redshifts and generally exhibit outflow velocities in the
100--500~\kms\ range
\citep[e.g.,][]{hec00,sha03,mar05,rup05,wei09,rub10,ste10}.  Thus, the
discovery of $|v|>1000$~\kms\ outflows in a sample of massive
($\textnormal{\mstar}\approx10^{11}$~\msun) post-starburst galaxies at
$z\sim0.6$ by \citet{tre07} suggested that a more energetic source,
such as feedback from an accreting supermassive black hole
\citep[e.g.,][]{sil98,dim05,deb12}, could have been responsible for
launching the winds \citep[see][for a recent review]{fab12}.

@@

In this Letter, we present results for a sample of massive galaxies at
$z\sim0.6$ that exhibit $\gtrsim1000$~\kms\ outflows, expanding on the
sample from \citet{tre07}.  We seek to test whether the energetic
outflows in these galaxies could have been driven by feedback from
starbursts with very large star-formation rate (SFR) surface densities
($\sigmasfr$).  Our analysis combines galaxy sizes obtained with the
Hubble Space Telescope (HST) with star-formation rates and stellar
masses estimated from WISE, Spitzer, SDSS, and GALEX photometry.

\begin{figure}[!t]
\includegraphics[angle=0,scale=0.41]{3seds.ps}
\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
  three galaxies with large SFR surface densities
  ($\sigmasfr>3000$~\units).  We show stellar population fits to the
  $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
  templates for dust emission \citep[M82 starburst, Arp 220 starburst,
    and obscured quasar;][]{pol07}.  The starburst templates provide
  reasonable fits to the $\lobs=12$ and 22~$\mu$m WISE photometry,
  while the quasar template does not.  Right: HST/WFC3 F814W images
  (probing $\lrest\approx5000$~\AA) showing that these galaxies are
  dominated by a compact nucleus.}
\label{fig:seds}
\end{figure}

@@

Our sample derives from 29 galaxies targeted for HST/WFC3 imaging in
programs 12019 and 12272 (PI: C. Tremonti).  Using the F814W filter on
the UVIS channel, which has $0.04\arcsec$ pixels and
$\textnormal{FWHM}=0.074\arcsec$, we obtained $4\times10$~min
exposures in a single orbit for each galaxy.  The dithered images were
processed with
MultiDrizzle\footnote{http://stsdas.stsci.edu/multidrizzle/} to
produce science mosaics with $0.02\arcsec$ pixels.  For each galaxy,
we use GALFIT \citep{pen02,pen10} to model the two-dimensional surface
brightness profile with a single Sersic component, using stars in the
images to construct the model point-spread function (PSF).  The Sersic
index (n) and effective radius ($r_e$) are free parameters in the
model.  In cases where the best-fit model returns $n>4$, we also fit
an $n=4$ de Vaucouleurs model \citep{dev48}, yielding a larger $r_e$
value (due to the covariance between $n$ and $r_e$), and we use these
these larger effective radii in our analysis.

@@

We gathered photometry from the All-Sky Release of the Wide-field
Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
General Release 6 from the Galaxy Evolution Explorer
\citep[GALEX,][]{mar05galex}.  We also obtained $5\times30$~sec
dithered exposures at 3.6~$\mu$m and 4.5~$\mu$m for all sources with
the Infrared Array Camera \citep{faz04} on the Spitzer Space Telescope
\citep{wer04} as part of General Observer program 60145 (PI:
C. Tremonti).  We used the post--basic calibrated data to perform
aperture photometry on all sources, and we also used the
APEX\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/tools/mopex/}
point-source extraction software for photometry of sources in crowded
fields.  All the photometry was corrected for Galactic extinction
based on the \citet{sch98} dust maps.  We show spectral energy
distributions (SEDs) for the three high-$\sigmasfr$ galaxies in
Figure~\ref{fig:seds}.

We estimate IR-based star-formation rates for the 25/29 galaxies with
WISE 12 or 22~$\mu$m detections by fitting \citet{cha01} templates to
their 12 and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
detections, this yields SFRs that agree with those obtained from the
\citet{ruj12} method based on 24~$\mu$m luminosity with a scatter of
0.05~dex.  We note that several authors have shown that the shape of
the IR SED for star-forming galaxies depends on the surface density of
star formation \citep[e.g.,][]{ruj11,elb11}, with more compact
starbursts having larger total-IR (8--1000~$\mu$m) to mid-IR
(8--24~$\mu$m) ratios.  The extreme $\sigmasfr$ values of our sample
imply large total-IR to mid-IR ratios, characteristic of the most
luminous galaxies in the local universe
\citep[e.g.,][]{cha01,dal02,rie09}.  If we used the most luminous
local templates for the 8/29 sources with SFRs in the ULIRG regime
($\sfrir>200$~\msun~yr$^{-1}$), we would obtain SFRs that are larger
by 0.5~dex than the values we adopt for this paper.

@@

While the SEDs (Figure~\ref{fig:seds}) and optical spectra
(Figure~\ref{fig:spectra}) for our sample indicate that their
bolometric output is dominated by star formation, it is worthwhile to
consider the level of ongoing AGN activity and its effect on our
measurements.  Among the high-$\sigmasfr$ galaxies, the strongest case
for detectable AGN emission can be made for J1506+5402, which has the
most luminous \oiii~$\lambda5007$ line among the 29 galaxies observed
by HST.  This source also has a weak \nev~$\lambda3426$ emission line,
which is associated with AGN activity \citep[e.g.,][]{abe08,gil10}.
It was observed with the Chandra X-ray Observatory (proposal ID
11700896, PI: C. Tremonti) and had four detected counts, corresponding
to a 0.5--8.0~keV X-ray luminosity of $10^{42.7}$~erg~s$^{-1}$ (see
P. Sell et al., in preparation for more details on the 12/29 galaxies
with Chandra observations).  Using the relationship between 2--10~keV
X-ray and 12.3~$\mu$m mid-IR luminosity for AGNs from \citet{gan09},
one would expect a source with
$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{42}$~erg~s$^{-1}$ to
have
$L_{\textnormal{\scriptsize{MIR}}}\approx7\times10^{42}$~erg~s$^{-1}$,
which is 400$\times$ smaller than observed luminosity for J1506+5402
($L_{\textnormal{\scriptsize{MIR}}}\approx3\times10^{45}$~erg~s$^{-1}$).
Based on its \oiii\ luminosity ($10^{42.1}$~erg~s$^{-1}$, a
significant fraction of which could be attributed to star formation)
and the calibration for type 1 AGNs from \citet{hec05}, one would
expect an intrinsic 2--10~keV luminosity of
$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{43}$~erg~s$^{-1}$,
suggesting absorption by a factor of $\sim10$ in the X-rays.  However,
even if the X-ray attenuation were a factor of 100, which is the
typical value for local Compton-thick AGNs \citep{dia09}, the expected
mid-IR AGN contribution would only be relevant at the $\lesssim$30\%
level.  Thus, similar to local ULIRGs \citep[e.g.,][]{far07}, the
bolometric output of the galaxies in our sample is dominated by star
formation, and we conclude that our results regarding large
$\sigmasfr$ values are not affected by AGN contamination.

@@

In addition to radiation pressure, we also expect significant momentum
flux from stellar winds and supernovae.  For example, a starburst with
$\textnormal{SFR}\approx200$~\msun~yr$^{-1}$ would be associated with
radiation pressure $L_{bol}/c\approx2\times10^{35}$~dyne and ram
pressure $\dot{p}\approx5$--$10\times10^{35}$~dyne from stellar winds
and supernovae \citep[e.g.,][]{lei92,hec93,lei99,vei05}.  Furthermore,
\citet{hec11} noted that such a large momentum injection
($\dot{p}\approx10^{35}$~dyne) from a small initial radius
$r_{0}\approx100$~pc could accelerate a cloud with column density
$N_{H}\approx10^{21}$~cm$^{-2}$ to a terminal velocity
$v_{\infty}\approx1800$~\kms.  Thus, the energetics of compact
starbursts are sufficient to produce the high-velocity outflows we
observe, and it is plausible that both radiation pressure on dust
grains and supernova ram pressure contribute to driving the winds.

@@

Finally, it is worthwhile to consider the implications of our results
for models of massive galaxy formation.  Simulaitons of major galaxy
mergers with large gas fractions ($f_{gas}\sim50$\%) can produce
$\textnormal{\mstar}\sim10^{11}$~\msun\ remnants with effective radii
$r_{e}\sim1$~kpc \citep[e.g.,][]{wuy10}, but our sample includes
galaxies of similar mass that are smaller by almost an order of
magnitude.  If these systems do evolve into quiescent elliptical
galaxies, it would be quite challenging for them to grow in size from
$r_e\sim0.1$~kpc to $r_e\sim5$~kpc to reach the local size--mass
relation \citep{shen03} in the $t\sim6$~Gyr since $z=0.6$.  For
comparison the compact, quiescent galaxies observed at $z\sim2$
\citep[e.g.,][]{tru07,van08} have $t\sim10$~Gyr to grow by a factor of
$\sim5$.  In this context, it is worth noting that the half-light
radius (ignoring dust attenuation) at rest-frame $V$ band (where our
HST observations probe) can be a factor of 5--10 smaller than the
half-mass radius for a gas-rich merger at final coalescence near the
peak of starburst activity \citep{wuy10}.  It would be worthwhile to
test for such size discrepancies and to pronbe the radial dependence
of the mass-to-light ratio for these galaxies by measuring sizes at
rest-frame near-IR wavelengths.

@@

\bibitem[Abazajian et al.(2009)]{aba09} Abazajian, K.~N.,
  Adelman-McCarthy, J.~K., Ag{\"u}eros, M.~A., et al.\ 2009, \apjs,
  182, 543
\bibitem[Abel \& Satyapal(2008)]{abe08} Abel, N.~P., \& Satyapal,
  S.\ 2008, \apj, 678, 686

@@

\bibitem[Dale \& Helou(2002)]{dal02} Dale, D.~A., \& Helou, G.\ 2002,
  \apj, 576, 159
\bibitem[de Vaucouleurs(1948)]{dev48} de Vaucouleurs, G.\ 1948,
  Annales d'Astrophysique, 11, 247
\bibitem[Debuhr et al.(2012)]{deb12} Debuhr, J., Quataert, E., \& Ma,
  C.-P.\ 2012, \mnras, 420, 2221

@@

\bibitem[Farrah et al.(2007)]{far07} Farrah, D., Bernard-Salas, J.,
  Spoon, H.~W.~W., et al.\ 2007, \apj, 667, 149
\bibitem[Fazio et al.(2004)]{faz04} Fazio, G.~G., Hora, J.~L., Allen,
  L.~E., et al.\ 2004, \apjs, 154, 10

@@

\bibitem[Heckman et al.(1993)]{hec93} Heckman, T.~M., Lehnert, M.~D.,
  \& Armus, L.\ 1993, The Environment and Evolution of Galaxies, 188,
  455

@@

\bibitem[Martin et al.(2005)]{mar05galex} Martin, D.~C., Fanson, J.,
  Schiminovich, D., et al.\ 2005, \apjl, 619, L1

@@

\bibitem[Peng et al.(2010)]{pen10} Peng, C.~Y., Ho, L.~C., Impey,
  C.~D., \& Rix, H.-W.\ 2010, \aj, 139, 2097

@@

\bibitem[Robaina et al.(2010)]{rob10} Robaina, A.~R., Bell, E.~F., van
  der Wel, A., et al.\ 2010, \apj, 719, 844

@@

\bibitem[Schlegel et al.(1998)]{sch98} Schlegel, D.~J., Finkbeiner,
  D.~P., \& Davis, M.\ 1998, \apj, 500, 525

@@

\bibitem[Werner et al.(2004)]{wer04} Werner, M.~W., Roellig, T.~L.,
  Low, F.~J., et al.\ 2004, \apjs, 154, 1
\bibitem[Wright et al.(2010)]{wri10} Wright, E.~L., Eisenhardt,
  P.~R.~M., Mainzer, A.~K., et al.\ 2010, \aj, 140, 1868

>>>>

Galactic winds are ubiquitous in star-forming galaxies at all
redshifts and generally exhibit outflow velocities in the
100--500~\kms\ range
\citep[e.g.,][]{hec00,sha03,mar05,rup05,wei09,rub10,ste10}.  Thus, the
discovery of $|v|>1000$~\kms\ outflows in a sample of massive
($\textnormal{\mstar}\approx10^{11}$~\msun) post-starburst galaxies at
$z\sim0.6$ by \citet{tre07} suggested that a more energetic source,
such as feedback from an accreting supermassive black hole
\citep[e.g.,][]{sil98,dim05}, could have been responsible for
launching the winds \citep[see][for a recent review]{fab12}.

@@

In this Letter, we present results for a sample of massive galaxies at
$z\sim0.6$ that exhibit $\gtrsim1000$~\kms\ outflows, expanding on the
sample from \citet{tre07}.  We seek to test whether the energetic
outflows in these galaxies could have been driven by feedback from
starbursts with very large star-formation rate (SFR) surface densities
($\sigmasfr$).  Our analysis combines galaxy sizes obtained with the
Hubble Space Telescope (HST) with star-formation rates and stellar
masses estimated using photometry from the Wide-field Infrared Survey
Explorer (WISE), the Spitzer Space Telescope, the Sloan Digital Sky
Survey (SDSS), and the Galaxy Evolution Explorer (GALEX).

\begin{figure}[!t]
\includegraphics[angle=0,scale=0.41]{3seds.ps}
\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
  three galaxies with large SFR surface densities
  ($\sigmasfr>3000$~\units).  We show stellar population fits to the
  $\lrest=0.1$--3~$\mu$m emission (black solid line) and two templates
  for dust emission \citep[M82 starburst, Arp 220 starburst;][]{pol07}
  scaled to match the $\lobs=4.6~\mu$m band.  The starburst templates
  provide reasonable fits to the $\lobs=12$ and 22~$\mu$m WISE
  photometry, while a quasar template does not.  Right: HST/WFC3 F814W
  images (probing $\lrest\approx5000$~\AA) showing that these galaxies
  are dominated by a compact nucleus.}
\label{fig:seds}
\end{figure}

@@

Our sample derives from 29 galaxies targeted for HST/WFC3 imaging in
programs 12019 and 12272 (PI: C. Tremonti).  Using the F814W filter on
the UVIS channel, which has $0.04\arcsec$ pixels and
$\textnormal{FWHM}=0.074\arcsec$, we obtained $4\times10$~min
exposures in a single orbit for each galaxy.  The dithered images were
processed with
MultiDrizzle\footnote{http://stsdas.stsci.edu/multidrizzle/} to
produce science mosaics with $0.02\arcsec$ pixels.  For each galaxy,
we use GALFIT \citep{pen02} to model the two-dimensional surface
brightness profile with a single Sersic component, using stars in the
images to construct the model point-spread function (PSF).  The Sersic
index (n) and effective radius ($r_e$) are free parameters in the
model.  In cases where the best-fit model returns $n>4$, we also fit
an $n=4$ de Vaucouleurs model, yielding a larger $r_e$ value (due to
the covariance between $n$ and $r_e$), and we use these these larger
effective radii in our analysis.

@@

% We gathered photometry from the All-Sky Release of the Wide-field
% Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
% Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
% General Release 6 from the Galaxy Evolution Explorer
% \citep[GALEX,][]{mar05galex}.  
We gathered photometry from the WISE All-Sky Release, the SDSS Seventh
Data Release, and GALEX General Release 6.  We also obtained
$5\times30$~sec dithered exposures at 3.6~$\mu$m and 4.5~$\mu$m for
all sources with the Infrared Array Camera on the Spitzer Space
Telescope as part of General Observer program 60145 (PI: C. Tremonti).
We used the post--basic calibrated data to perform aperture photometry
on all sources, and we also used the
APEX\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/tools/mopex/}
point-source extraction software for photometry of sources in crowded
fields.  We show spectral energy distributions (SEDs) for the three
high-$\sigmasfr$ galaxies in Figure~\ref{fig:seds}.

% All the photometry was corrected for Galactic extinction
% based on the \citet{sch98} dust maps.

We estimate IR-based star-formation rates for the 25/29 galaxies with
WISE 12 or 22~$\mu$m detections by fitting \citet{cha01} templates to
their 12 and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
detections, this yields SFRs that agree with those obtained from the
\citet{ruj12} method based on 24~$\mu$m luminosity with a scatter of
0.05~dex.  We note that several authors have shown that the shape of
the IR SED for star-forming galaxies depends on the surface density of
star formation \citep[e.g.,][]{ruj11,elb11}, with more compact
starbursts having larger total-IR (8--1000~$\mu$m) to mid-IR
(8--24~$\mu$m) ratios.  The extreme $\sigmasfr$ values of our sample
imply large total-IR to mid-IR ratios, characteristic of the most
luminous galaxies in the local universe
\citep[e.g.,][]{rie09}.  If we used the most luminous
local templates for the 8/29 sources with SFRs in the ULIRG regime
($\sfrir>200$~\msun~yr$^{-1}$), we would obtain SFRs that are larger
by 0.5~dex than the values we adopt for this paper.

@@

While the SEDs (Figure~\ref{fig:seds}) and optical spectra
(Figure~\ref{fig:spectra}) for our sample indicate that their
bolometric output is dominated by star formation, it is worthwhile to
consider the level of ongoing AGN activity and its effect on our
measurements.  Among the high-$\sigmasfr$ galaxies, the strongest case
for detectable AGN emission can be made for J1506+5402, which has the
most luminous \oiii~$\lambda5007$ line among the 29 galaxies observed
by HST.  This source also has a weak \nev~$\lambda3426$ emission line,
which is associated with AGN activity \citep[e.g.,][]{gil10}.  It was
observed with the Chandra X-ray Observatory (proposal ID 11700896, PI:
C. Tremonti) and had four detected counts, corresponding to a
0.5--8.0~keV X-ray luminosity of $10^{42.7}$~erg~s$^{-1}$ (see P. Sell
et al., in preparation for more details on the 12/29 galaxies with
Chandra observations).  Using the relationship between 2--10~keV X-ray
and 12.3~$\mu$m mid-IR luminosity for AGNs from \citet{gan09}, one
would expect a source with
$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{42}$~erg~s$^{-1}$ to
have
$L_{\textnormal{\scriptsize{MIR}}}\approx7\times10^{42}$~erg~s$^{-1}$,
which is 400$\times$ smaller than observed luminosity for J1506+5402
($L_{\textnormal{\scriptsize{MIR}}}\approx3\times10^{45}$~erg~s$^{-1}$).
Based on its \oiii\ luminosity ($10^{42.1}$~erg~s$^{-1}$, a
significant fraction of which could be attributed to star formation)
and the calibration for type 1 AGNs from \citet{hec05}, one would
expect an intrinsic 2--10~keV luminosity of
$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{43}$~erg~s$^{-1}$,
suggesting absorption by a factor of $\sim10$ in the X-rays.  However,
even if the X-ray attenuation were a factor of 100, which is the
typical value for local Compton-thick AGNs \citep{dia09}, the expected
mid-IR AGN contribution would only be relevant at the $\lesssim$30\%
level.  We conclude that the bolometric output of the galaxies in our
sample is dominated by star and we that our results regarding large
$\sigmasfr$ values are not affected by AGN contamination.

% Thus, similar to local ULIRGs \citep[e.g.,][]{far07}, the
% bolometric output of the galaxies in our sample is dominated by star
% formation, and we conclude that our results regarding large
% $\sigmasfr$ values are not affected by AGN contamination.

@@

In addition to radiation pressure, we also expect significant momentum
flux from stellar winds and supernovae.  For example, a starburst with
$\textnormal{SFR}\approx200$~\msun~yr$^{-1}$ would be associated with
radiation pressure $L_{bol}/c\approx2\times10^{35}$~dyne and ram
pressure $\dot{p}\approx5$--$10\times10^{35}$~dyne from stellar winds
and supernovae \citep[e.g.,][]{lei92,lei99,vei05}.  Furthermore,
\citet{hec11} noted that such a large momentum injection
($\dot{p}\approx10^{35}$~dyne) from a small initial radius
$r_{0}\approx100$~pc could accelerate a cloud with column density
$N_{H}\approx10^{21}$~cm$^{-2}$ to a terminal velocity
$v_{\infty}\approx1800$~\kms.  Thus, the energetics of compact
starbursts are sufficient to produce the high-velocity outflows we
observe, and it is plausible that both radiation pressure on dust
grains and supernova ram pressure contribute to driving the winds.

@@

Finally, it is worthwhile to consider the implications of our results
for models of massive galaxy formation.  Simulaitons of major galaxy
mergers with large gas fractions ($f_{gas}\sim50$\%) can produce
$\textnormal{\mstar}\sim10^{11}$~\msun\ remnants with effective radii
$r_{e}\sim1$~kpc \citep[e.g.,][]{wuy10}, but our sample includes
galaxies of similar mass that are smaller by almost an order of
magnitude.  If these systems do evolve into quiescent elliptical
galaxies, it would be quite challenging for them to grow in size from
$r_e\sim0.1$~kpc to $r_e\sim5$~kpc to reach the local size--mass
relation \citep{she03} in the $t\sim6$~Gyr since $z=0.6$.  For
comparison the compact, quiescent galaxies observed at $z\sim2$
\citep[e.g.,][]{tru07,van08} have $t\sim10$~Gyr to grow by a factor of
$\sim5$.  In this context, it is worth noting that the half-light
radius (ignoring dust attenuation) at rest-frame $V$ band (where our
HST observations probe) can be a factor of 5--10 smaller than the
half-mass radius for a gas-rich merger at final coalescence near the
peak of starburst activity \citep{wuy10}.  It would be worthwhile to
test for such size discrepancies and to pronbe the radial dependence
of the mass-to-light ratio for these galaxies by measuring sizes at
rest-frame near-IR wavelengths.

@@

%\bibitem[Abazajian et al.(2009)]{aba09} Abazajian, K.~N.,
%  Adelman-McCarthy, J.~K., Ag{\"u}eros, M.~A., et al.\ 2009, \apjs,
%  182, 543
%\bibitem[Abel \& Satyapal(2008)]{abe08} Abel, N.~P., \& Satyapal,
%  S.\ 2008, \apj, 678, 686

@@

%\bibitem[Dale \& Helou(2002)]{dal02} Dale, D.~A., \& Helou, G.\ 2002,
%  \apj, 576, 159
%\bibitem[de Vaucouleurs(1948)]{dev48} de Vaucouleurs, G.\ 1948,
%  Annales d'Astrophysique, 11, 247
%\bibitem[Debuhr et al.(2012)]{deb12} Debuhr, J., Quataert, E., \& Ma,
%  C.-P.\ 2012, \mnras, 420, 2221

@@

%\bibitem[Farrah et al.(2007)]{far07} Farrah, D., Bernard-Salas, J.,
%  Spoon, H.~W.~W., et al.\ 2007, \apj, 667, 149
%\bibitem[Fazio et al.(2004)]{faz04} Fazio, G.~G., Hora, J.~L., Allen,
%x  L.~E., et al.\ 2004, \apjs, 154, 10

@@

%\bibitem[Heckman et al.(1993)]{hec93} Heckman, T.~M., Lehnert, M.~D.,
%  \& Armus, L.\ 1993, The Environment and Evolution of Galaxies, 188,
%  455

@@

%\bibitem[Martin et al.(2005)]{mar05galex} Martin, D.~C., Fanson, J.,
%  Schiminovich, D., et al.\ 2005, \apjl, 619, L1

@@

%\bibitem[Peng et al.(2010)]{pen10} Peng, C.~Y., Ho, L.~C., Impey,
%  C.~D., \& Rix, H.-W.\ 2010, \aj, 139, 2097

@@

@@

%\bibitem[Schlegel et al.(1998)]{sch98} Schlegel, D.~J., Finkbeiner,
%  D.~P., \& Davis, M.\ 1998, \apj, 500, 525

@@

%\bibitem[Werner et al.(2004)]{wer04} Werner, M.~W., Roellig, T.~L.,
%  Low, F.~J., et al.\ 2004, \apjs, 154, 1
%\bibitem[Wright et al.(2010)]{wri10} Wright, E.~L., Eisenhardt,
%  P.~R.~M., Mainzer, A.~K., et al.\ 2010, \aj, 140, 1868
